---
title: "Assignment_5"
author: "Dengcheng Chen"
date: "04/17/2022"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

**Data Preprocessing. Remove all cereals with missing values**

```{r}
library(readr)
C.df <-read.csv('Cereals.csv',header=TRUE)
C.df <- na.omit(C.df)
rownames(C.df) <- C.df$name
C.df$name = NULL
C.df <- C.df[,3:15]
C.df <- scale(C.df)
summary(C.df)
```
**Q1**Apply hierarchical clustering to the data using Euclidean distance to the normalized
measurements. Use Agnes to compare the clustering from  single linkage, complete
linkage, average linkage, and Ward. Choose the best method.

```{r}
library(factoextra)
dist <- dist(C.df, method = "euclidean")
HC_C <- hclust(dist, method = "complete")
HC_S <- hclust(dist, method = "single")
HC_A <- hclust(dist, method = "average")
HC_W <- hclust(dist, method = "ward.D2")
plot(HC_C,cex=0.5,hang=0.1)
plot(HC_S,cex=0.5,hang=0.1)
plot(HC_A,cex=0.5,hang=0.1)
plot(HC_W,cex=0.5,hang=0.1)
```
**Q2**How many clusters would you choose?
```{r}
plot(HC_W,cex=0.5,hang=0.1)
rect.hclust(HC_W, k = 5, border = 1:5)
plot(HC_W,cex=0.5,hang=0.1)
rect.hclust(HC_W, k = 4, border = 1:4)
plot(HC_W,cex=0.5,hang=0.1)
rect.hclust(HC_W, k = 6, border = 1:6)
plot(HC_W,cex=0.5,hang=0.1)
rect.hclust(HC_W, k = 7, border = 1:7)
```
I will choose 6 clusters.

**Q3**The elementary public schools would like to choose a set of cereals to include in their 
daily cafeterias. Every day a different cereal is offered, but all cereals should support a 
healthy diet. For this goal, you are requested to find a cluster of “healthy cereals.” 

For elementary public schools,the definition of he health should be high protein, high vitamin, and reasonable calories. So, I will choose the 1st cluster counting form the right as the “healthy cereals” 



