---
title: "Assignment_2"
author: "Dengcheng Chen"
date: "2022/2/20"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---

```{r}
library(readr)
Ubank <- read_delim(file = 'UniversalBank.csv',delim=',')
library(reshape)
Ubank <- rename(Ubank,c(`Personal Loan` = 'PL','Securities Account'='SA','CD Account'='CDA'))
names(Ubank)
summary(Ubank)
```


```{r}
Ubank$ID <-  NULL
Ubank$`ZIP Code` <- NULL

Ubank$Education = as.factor(Ubank$Education)
Ubank$PL = as.factor(Ubank$PL)
summary(Ubank)
```
```{r}
library(caret)
library(class)

dummies <- dummyVars(PL ~ ., data = Ubank)
Ubank_dummy <- as.data.frame(predict(dummies, newdata= Ubank))
head(Ubank_dummy)
```



```{r}
Norm_model <- preProcess(Ubank_dummy,method = c("center", "scale"))
Ubank_norm = predict(Norm_model,Ubank_dummy)
summary(Ubank_norm)
```
```{r}
Ubank_norm$PL=Ubank$PL
```


```{r}
Train_Index = createDataPartition(Ubank$PL,p=0.6, list=FALSE)
Train.df = Ubank_norm[Train_Index,]
Validation.df = Ubank_norm[-Train_Index,]
```

*Q1* Age = 40, Experience = 10, Income = 84, Family = 2, CCAvg = 2, Education_1 = 0, Education_2 = 1, Education_3 = 0, Mortgage = 0, Securities Account = 0, CD Account = 0, Online = 1, and
CreditCard = 1. Perform a k-NN classification with all predictors except ID and ZIP code
using k = 1. Remember to transform categorical predictors with more than two categories
into dummy variables first. Specify the success class as 1 (loan acceptance), and use the
default cutoff value of 0.5. How would this customer be classified?

```{r}
To_Predict=data.frame(Age=40, Experience = 10, Income = 84, Family = 2, CCAvg = 2, 
                      Education.1 = 0, Education.2 = 1, Education.3 = 0, Mortgage = 0,
                     SA = 0, CDA = 0, Online = 1,CreditCard = 1)
                   
print(To_Predict)
```

```{r}
To_Predict_norm <- predict(Norm_model,To_Predict)
print(To_Predict_norm)
```
```{r}
Prediction <- knn(train = Train.df[1:13],
                  test = To_Predict_norm[1:13],
                  cl=Train.df$PL,
                  k=1)
print(Prediction)
```

Addicting to the result, the customer will not be the targeted one.

*Q2* What is a choice of k that balances between overfitting and ignoring the predictor 
information?

```{r}
set.seed(123)
fitControl <- trainControl(method = "repeatedcv",
                           number = 3,
                           repeats = 2)
searchGrid=expand.grid(k = 1:15)
Knn.model=train(PL~., 
                data=Train.df,
                method='knn',
                tuneGrid=searchGrid,
                trControl = fitControl,)

Knn.model
```
*Q3* Show the confusion matrix for the validation data that results from using the best k.

```{r}
predictions<-predict(Knn.model,Validation.df)
confusionMatrix(predictions,Validation.df$PL)
```
*Q4* Consider the following customer: Age = 40, Experience = 10, Income = 84,
Family = 2, CCAvg = 2, Education_1 = 0, Education_2 = 1, Education_3 = 0,
Mortgage = 0, Securities Account = 0, CD Account = 0, Online = 1 and Credit
Card = 1. Classify the customer using the best k.

```{r}
To_Predict=data.frame(Age=40, Experience = 10, Income = 84, Family = 2, CCAvg = 2, 
                      Education.1 = 0, Education.2 = 1, Education.3 = 0, Mortgage = 0,
                     SA = 0, CDA = 0, Online = 1,CreditCard = 1)
To_Predict_norm=predict(Norm_model,To_Predict)
predict(Knn.model,To_Predict_norm)
```

Also, this cumstomer is not the targeted one.
